National demographic-disturbance relationships and local monitoring both reduce uncertainty in projections of boreal caribou population viability: tools to support monitoring decisions

### 2023-12-15 analysis/paper/paper.Rmd
Tweaks, and adding simulation set without composition bias.

```{r figStatusErrors, fig.cap="The probability of a correct status assessment varies with the amount of anthropogenic disturbance (columns), the number of years projected (rows), and monitoring effort (see Figure \\@ref(fig:figDisturbance) for scenarios). Probabilities are calculated for 200 example population trajectories (see example trajectories in Figure \\@ref(fig:exampleTrajectories)). For each example population, the status assessment is correct if the Bayesian posterior mean and the true population growth rate are both less than or equal to 0.99, or both greater than 0.99. When disturbance is very high or very low the probability of correct status assessment is high even without local monitoring. Where disturbance is moderate, increasing the number of years of monitoring and the number of collars reduces uncertainty, but there are diminishing returns on additional monitoring as sample size increases. In these examples the apparent number of adult females per collared animal in composition survey $w$ is 6; varying this parameter does not alter qualitative outcomes (supplement D).", cache=TRUE}
knitr::include_graphics(here::here("figs/forPaper/powercmult6ay3aSf1.png"))
```

```{r figDiffs, fig.cap="The distribution of differences between the true population growth rate and the Bayesian posterior mean growth rate varies with the amount of anthropogenic disturbance (columns), the number of years projected (rows), and monitoring effort (see Figure \\@ref(fig:figDisturbance) for scenarios). Differences are calculated for 200 example population trajectories (see example trajectories in Figure \\@ref(fig:exampleTrajectories)). Differences decrease as the number of years of monitoring and the number of collars increase. Differences are larger when the projection period is longer. Differences are also higher when anthropogenic disturbance is high because stochastic variation in population growth rate is higher when population sizes are small. In these examples the apparent number of adult females per collared animal in composition survey $w$ is 6, and collars are renewed each year.", cache=TRUE}
knitr::include_graphics(here::here("figs/forPaper/diffscmult6ay3aSf1.png"))
```

>>>>

```{r figStatusErrors, fig.cap="The probability of a correct status assessment varies with the amount of anthropogenic disturbance (columns), the number of years projected (rows), and monitoring effort (see Figure \\@ref(fig:figDisturbance) for scenarios). Probabilities are calculated for 200 example population trajectories (see example trajectories in Figure \\@ref(fig:exampleTrajectories)). For each example population, the status assessment is correct if the Bayesian posterior mean and the true population growth rate are both less than or equal to 0.99, or both greater than 0.99. When disturbance is very high or very low the probability of correct status assessment is high even without local monitoring. Where disturbance is moderate, increasing the number of years of monitoring and the number of collars reduces uncertainty, but there are diminishing returns on additional monitoring as sample size increases. In these examples the apparent number of adult females per collared animal in composition survey $w$ is 6; varying this parameter does not qualitatively alter outcomes (supplement D).", cache=TRUE}
knitr::include_graphics(here::here("figs/forPaper/powercmult6ay3aSf1.png"))
```

```{r figDiffs, fig.cap="The distribution of differences between true population growth rates and Bayesian posterior mean growth rates varies with the amount of anthropogenic disturbance (columns), the number of years projected (rows), and monitoring effort (see Figure \\@ref(fig:figDisturbance) for scenarios). Differences are calculated for 200 example population trajectories (see example trajectories in Figure \\@ref(fig:exampleTrajectories)). Differences decrease as the number of years of monitoring and the number of collars increase. Differences are larger when the projection period is longer. Differences are also larger when anthropogenic disturbance is high because stochastic variation in population growth rate is high for small populations. In these examples the apparent number of adult females per collared animal in composition survey $w$ is 6, and collars are renewed each year.", cache=TRUE}
knitr::include_graphics(here::here("figs/forPaper/diffscmult6ay3aSf1.png"))
```
